### 2022-09-29 sections/introduction.tex

The CMS Collaboration performed a similar search using  
$H\to b\bar{b}$ decays~\cite{Sirunyan:2017uae} with 35.9 fb$^{-1}$ of data at $\sqrt{s}=13~\tev$, resulting 
in upper limits of $\BR(t\to cH)<0.47\%$ and $\BR(t\to uH)<0.47\%$, in each case neglecting the other decay mode.
%Compared with previous searches, 
The search in Ref.~\cite{Sirunyan:2017uae} also considers the contribution to the signal from 
$pp \to tH$ production~\cite{Greljo:2014dka}. 
CMS subsequently updated their search for $tqH$ in the $H\to b\bar{b}$ channel using
the full Run~2 dataset, obtaining observed (expected) upper limits of  $\BR(t\to cH) < 9.4\times10^{-4}\, (8.6\times10^{-4})$
and $\BR(t\to uH) < 7.9\times10^{-4}\, (1.1\times10^{-3})$~\cite{CMS:2021gfa}.
%CMS also recently reported a search for $tqH$ in the $H\rightarrow \gamma\gamma$ mode using the full Run-2 data and set observed(expected) upper limits on $\mathcal{B}(t\to Hu)$ of $1.9\times10^{-4}(3.1\times10^{-4})$ and $\mathcal{B}(t\to Hc)$ of $7.3\times10^{-4}(5.1\times10^{-4})$~\cite{CMS-PAS-TOP-20-007}.

\begin{table}[t!]
\caption{\small{Summary of 95\% CL upper limits on $\BR(t \to cH)$ and $\BR(t \to uH)$ obtained by the ATLAS and CMS collaborations with Run~2 data. Each limit is obtained assuming the other branching ratio is zero.}}
\begin{center}
\small 
\begin{tabular}{ccccc}
\toprule\toprule
& &\multirow{2}{*}{$\mathcal{L}$ [fb$^{-1}$]} & \multicolumn{2}{c}{95\% CL observed upper limits}  \\
& & 										    & \multicolumn{1}{c}{on $\BR(t \to cH)$}            & \multicolumn{1}{c}{on $\BR(t \to uH)$} \\
\midrule
\multirow{5}{*}{ATLAS}
& $H \to b\bar{b}$~\cite{fcnc36}                                          & 36.1         & $4.2 \times 10^{-3}$ & $5.2 \times 10^{-3}$ \\
& $H \to \gamma\gamma$~\cite{Aaboud:2017mfd}                              & 36.1         & $2.2 \times 10^{-3}$  & $2.4 \times 10^{-3}$  \\
& $H \to \tau\tau$ ($\lephad$, $\hadhad$)~\cite{fcnc36}                   & 36.1         & $1.9 \times 10^{-3}$  & $1.7 \times 10^{-3}$  \\ 
& $H \to WW^*, \tau\tau, ZZ^*$ ($2\ell$SS, $3\ell$)~\cite{Aaboud:2018pob} & 36.1         & $1.6 \times 10^{-3}$  & $1.9 \times 10^{-3}$\\ 
& Combination~\cite{fcnc36}                                               & 36.1         & $1.1 \times 10^{-3}$  & $1.2 \times 10^{-3}$  \\\midrule
\multirow{2}{*}{CMS} 
& $H \to b\bar{b}$~\cite{Sirunyan:2017uae}                                & 35.9         & $4.7 \times 10^{-3}$  & $4.7 \times 10^{-3}$  \\
& $H \to b\bar{b}$~\cite{CMS:2021gfa}                                     & 137~~~~~          & $9.4 \times 10^{-4}$  & $7.9 \times 10^{-4}$  \\
%& $H \to \gamma\gamma$~\cite{CMS-PAS-TOP-20-007}                          & 137          & $7.3 \times 10^{-4}$  & $1.9 \times 10^{-4}$  \\
% 
\bottomrule\bottomrule
\end{tabular}
\label{tab:limits_summary_ref}
\end{center}
\end{table}

>>>>

The CMS Collaboration performed a similar search using  
$H\to b\bar{b}$ decays~\cite{Sirunyan:2017uae} with 35.9 fb$^{-1}$ of data at $\sqrt{s}=13~\tev$, resulting 
in upper limits of $\BR(t\to cH)<0.47\%$ and $\BR(t\to uH)<0.47\%$, in each case neglecting the other decay mode.
%Compared with previous searches, 
The search in Ref.~\cite{Sirunyan:2017uae} also considers the contribution to the signal from 
$pp \to tH$ production~\cite{Greljo:2014dka}. 
CMS subsequently updated their search for $tqH$ in the $H\to b\bar{b}$ channel using
the full Run~2 dataset, obtaining observed (expected) upper limits of  $\BR(t\to cH) < 9.4\times10^{-4}\, (8.6\times10^{-4})$
and $\BR(t\to uH) < 7.9\times10^{-4}\, (1.1\times10^{-3})$~\cite{CMS:2021gfa}.
CMS also recently reported a search for $tqH$ in the $H\rightarrow \gamma\gamma$ mode using the full Run-2 data and set observed(expected) upper limits on $\mathcal{B}(t\to Hu)$ of $1.9\times10^{-4}(3.1\times10^{-4})$ and $\mathcal{B}(t\to Hc)$ of $7.3\times10^{-4}(5.1\times10^{-4})$~\cite{CMS-PAS-TOP-20-007}.

\begin{table}[t!]
\caption{\small{Summary of 95\% CL upper limits on $\BR(t \to cH)$ and $\BR(t \to uH)$ obtained by the ATLAS and CMS collaborations with Run~2 data. Each limit is obtained assuming the other branching ratio is zero.}}
\begin{center}
\small 
\begin{tabular}{ccccc}
\toprule\toprule
& &\multirow{2}{*}{$\mathcal{L}$ [fb$^{-1}$]} & \multicolumn{2}{c}{95\% CL observed upper limits}  \\
& & 										    & \multicolumn{1}{c}{on $\BR(t \to cH)$}            & \multicolumn{1}{c}{on $\BR(t \to uH)$} \\
\midrule
\multirow{5}{*}{ATLAS}
& $H \to b\bar{b}$~\cite{fcnc36}                                          & 36.1         & $4.2 \times 10^{-3}$ & $5.2 \times 10^{-3}$ \\
& $H \to \gamma\gamma$~\cite{Aaboud:2017mfd}                              & 36.1         & $2.2 \times 10^{-3}$  & $2.4 \times 10^{-3}$  \\
& $H \to \tau\tau$ ($\lephad$, $\hadhad$)~\cite{fcnc36}                   & 36.1         & $1.9 \times 10^{-3}$  & $1.7 \times 10^{-3}$  \\ 
& $H \to WW^*, \tau\tau, ZZ^*$ ($2\ell$SS, $3\ell$)~\cite{Aaboud:2018pob} & 36.1         & $1.6 \times 10^{-3}$  & $1.9 \times 10^{-3}$\\ 
& Combination~\cite{fcnc36}                                               & 36.1         & $1.1 \times 10^{-3}$  & $1.2 \times 10^{-3}$  \\\midrule
\multirow{2}{*}{CMS} 
& $H \to b\bar{b}$~\cite{Sirunyan:2017uae}                                & 35.9         & $4.7 \times 10^{-3}$  & $4.7 \times 10^{-3}$  \\
& $H \to b\bar{b}$~\cite{CMS:2021gfa}                                     & 137~~~~~          & $9.4 \times 10^{-4}$  & $7.9 \times 10^{-4}$  \\
& $H \to \gamma\gamma$~\cite{CMS-PAS-TOP-20-007}                          & 137          & $7.3 \times 10^{-4}$  & $1.9 \times 10^{-4}$  \\
% 
\bottomrule\bottomrule
\end{tabular}
\label{tab:limits_summary_ref}
\end{center}
\end{table}
